Typed Functional Genetic Programming

### 2013-07-17 tex/thesis.tex
[tex]

@@

Genetic programming (GP) is an AI technique, which falls into 
broader category of evolutionary algorithms --- 
mataheuristic search algorithms inspired by 
biological evolution by natural selection.
I dare say many people perceive its beauty in the fact that GP is
a computer program constructing other computer programs 
with desired properties by breeding them. 
It is also pretty successful technique in a number of areas. 
And perhaps that is why GP has become very popular.

>>>>

% možná místo classical GP řikat standard GP jako montana95

@@

%	Seznamte se s typovanými lambda kalkuly [1] 
%	a s jejich praktickou implementací [5]. 
%	Prostudujte standardní techniky genetického 
%	programování [2-4]. Navrhněte a implementujte 
%	prototyp systému řešící úlohu genetického 
%	programování nad typovaným funkcionálním 
%	jazykem. Porovnejte dosažené výsledky 
%	v závislosti na zvolených vstupních parametrech.

Genetic programming (GP) is an AI technique, which falls into 
broader category of evolutionary algorithms --- 
mataheuristic search algorithms inspired by 
biological evolution by natural selection.
I dare say many people perceive its beauty in the fact that GP is
a computer program constructing other computer programs 
%(property sometimes called \textit{automatic programming}) 
with desired properties by breeding them. 
It is also pretty successful technique in a number of areas. 
And perhaps that is why GP has become very popular.

GP constructs the population of solution programs from 
two sets of building blocks; set F of functions 
and set T of constants and variables. 
In classical GP \textit{type consistency} of those 
building blocks is required, property also called \textit{closure}.
This means that all functions must accept
